2024 US Presidential Election Forecast Model

### 2024-11-02 paper/paper.qmd

---
title: "2024 US Presidential Election Forecast Model"
subtitle: "My subtitle if needed"
author: 
  - Viet Nguyen
  - Yihang Xu
  - Doran Wang
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

clean_data <- read.csv("/Users/nguyenviet/Documents/term-paper-2/data/01-raw_data/clean_data.csv")

@@

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

@@

>>>>

---
title: "2024 US Presidential Election Forecast Model"
subtitle: "My subtitle if needed"
author: 
  - Viet Nguyen
  - Yihang Xu
  - Doran Wang
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: true
toc-title: "Table of Contents"
number-sections: true
bibliography: references.bib
---

@@

clean_data <- read_csv("../data/01-raw_data/clean_data.csv")
nyt_data <- read_csv("../data/02-analysis_data/NYT_data.csv")
```

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-cleaned_data
#| tbl-cap: "Sample Cleaned Data"
#| warning: false

clean_data |>
  head(5) |>
  kable(col.names = c("Pollster","Display Name","Pollster Rating ID","Grade","Poll Score", "Transparency Score","State","Start Date","End_Date", "Sample Size", "Election Date", "Party", "Answer","Candidate Name","Percentage"),
    booktabs = TRUE
  )

```{r}
#| label: fig-distribution_Answers
#| fig-cap: Distribution of Answers
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-histrpct
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

@@

# Discussion of the survey’s methodology of Siena/NYT

## Population, Frame, and Sample

-Population:

-Frame:

-Sample:
a topline sample size of at least 100

## Sample Recruitment Method

## Sampling Approach's trade-offs

-Strengths:

-Weaknesses:

## How is non-response handled

## What is good and bad about the questionnaire

### Advantages

### Disadvantages

\newpage
